\documentclass[8pt]{article}
\usepackage{array, xcolor}
\usepackage[margin=2cm]{geometry}
\usepackage{longtable}
\usepackage{makecell}
\usepackage{hyperref}
\usepackage{multicol}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
}
\definecolor{lightgray}{gray}{0.5}
\newcolumntype{L}{>{\raggedleft}p{0.5\textwidth}}
\newcolumntype{R}{p{0.5\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\title{\bfseries Farzad Sadeghi}
\author{farzadsadeghi@protonmail.ch}
\date{2021/01/08}
\begin{document}
\begin{multicols}{2}
  \maketitle
  \begin{center}
    \begin{minipage}[ht]{0.2\textwidth}{\centering}
      \vspace*{\fill}
      \centering
      Tehran, Iran\\
      +98 9999 9999999
      \centering
      \vspace*{\fill}
    \end{minipage}
  \end{center}

  \section*{Professional Experience}
  \bf Erfan Salamat (Tehran, Iran)\\
  Nov. 2020--Feb. 2021\\
  4 months\\
  \normalfont Backened Developer. Developed a GIS and Notification microservice using Golang(go-kit). Containerized the entire required stack for the said microservices using Docker.\\[5pt]
  \bf Maharan International (Tehran, Iran)\\
  Feb. 2019--Oct. 2020\\
  19 months\\
  \normalfont Requirement manager, designer and developer for ERTMS/ETCS DMI.\\[5pt]
  \bf Truebit (Remote, 3 time-zones)\\
  July 2017--Nov. 2017\\
  5 months\\
  \normalfont developed Truebit's WASM interpreter and smart contracts. Also managed the CI for the repositories.\\[5pt]
  \bf Iranian Electronics Industry Engineering Corp (Tehran, Iran)\\
  Sept. 2016--Nov. 2016\\
  2 months\\
  \normalfont The role primarily included devising the coding standard and style for the company.\\[5pt]
  \bf NEAT (Rome, Italy)\\
  May 2016--July 2016\\
  3 months\\
  \normalfont Wrote an automatic refactoring tool using Clang(Libtooling) in C++. The tool would be the last piece of an automated model-driven development process for safety-critical systems.\\[5pt]
  \bf Crouse (Tehran, Iran)\\
  July 2014--March 2016\\
  21 months\\
  \normalfont Embedded software developer, Safety-critical applications: Design, implementation and automation. The Software team’s ISO 26262 representative.\\[5pt]
  \bf Safir Language Academy (Tehran, Iran)\\
  August 2010--March 2012\\
  20 months\\
  \normalfont English Teacher - Later on specifically IELTS teacher.\\[5pt]

  \section*{Skills}
  \bf Software Design \normalfont Safety-critical software design.\\[5pt]
  \bf Requirement Analysis \normalfont{} Derived the functional and technical software requirements from the ERTMS/ETCS DMI system requirements for our implementation.\\[5pt]
  \bf CI \normalfont Appveyor for windows(cygwin-only) and TrvisCI for linux.\\[5pt]
  \bf UML \normalfont Requirement Modelling.\\[5pt]
  \bf Tooling \normalfont Static analysis tools using clang libraries.\\[5pt]
  \bf Automation \normalfont Python and the terminal.\\[5pt]
  \bf Containerization \normalfont Docker\\[5pt]
  \bf DB \normalfont Postgresql, MongoDB, Redis\\[5pt]

  \section*{Programming Languages}
  \bf Languages: \normalfont C, C++, Go\\[5pt]
  \bf Scripting Languages: \normalfont Python, Lua\\[5pt]
  \bf Other: \normalfont Bash, AWK, Cmake, Make, Docker\\[5pt]

  \section*{Languages}
  \bf English: {\normalfont Native-like}\\
  \bf Persian: {\normalfont Native}\\
  \bf Azerbaijani: {\normalfont Native}\\
  \normalfont German: Beginner\\

  \section*{Education}
  2007--2013 Bachelor's in Electrical Engineering, Iran University of Science and Technology, Tehran, Iran.\\[5pt]
  \bf Thesis: \normalfont Determining the frequency of an audio signal using phase derivation in real time, design and implementation using an FPGA.

  \section*{Role Breakdown}
  \bf Backend Developer\\ \normalfont Developed a GIS microservice based on the OSM stack. Containerized an entire geoserver stack (geoserver, tile server, static image server, DB) so that we could rely on our own stack. Developed a notification microservice using golang and Mongodb(with Percona memory engine).
  \\[5pt]\\
  \bf ERTMS / ETCS DMI Development\\ \normalfont Split the DMI into two subsystems. Designed and implemented the software for the component on the "kernel" side. Wrote a tool that made the requirements' traceability files by gathering special comments from the C source files. Wrote a tool that determines all the sub-fields of aggregate types used in the function and the functions it calls(required for testing).
  \\[5pt]\\
  \bf Embedded Safety-Critical Development\\ \normalfont Wrote the SRS and the SDD for the DSP algorithm, then implemented the DSP algorithm for a safety-critical hard real-time embedded system.
  \\[5pt]\\
  \bf Code Generation\\ \begin{itemize}\normalfont
    \vspace{-\baselineskip}
  \item Wrote A tool that generates binary file (WASM, ...) parsers in C.
  \item Wrote another tool that generates the C code necessary to add a C structure to Lua as a Lua table.
\end{itemize}
\bf Automation and Tooling\\ \begin{itemize}\normalfont
  \vspace{-\baselineskip}
\item Developed a Misra-C:2004 rule checker(open-source project) using Clang's Libtooling.
\item Developed a source code obfuscation tool(open-source project) using Clang's Libtooling.
\item Developed an interactive CLI tool aimed at object code manipulation(open-source project) in C++/C with Lua as it's scripting language. The tool also has Python embedded in it for rapid prototyping.
\item Automated the traceability matrix generation using libclang's Python bindings.
\item Automated the regression testing for a project I was involved in.
\item Automated the calculation of the WCET for all implemented functions through the use of of a Python script and an XML description file.
  \end{itemize}
  \bf Automatic Refactoring\\ \normalfont Wrote an automatic refactoring tool using Clang's Libtooling for C.\\[5pt]
  \\
  \bf Defensive Programming / Safety-Aware Software Design\\ \normalfont Studied/Implemented defensive programming practices, coding style and guidelines. Explored the use of FMEA and FTA for the software domain.\\[5pt]
  \\
  \bf AUTOSAR\\ \normalfont Studied AUTOSAR SWC and RTE.\\[5pt]
  \\
  \bf ISO 26262\\ \normalfont Studied the software section of the standard. I was also the software's group's representative for the study/review meetings held with the hardware and system teams on ISO 26262.\\[5pt]

  \section*{Links}
  {\bf \href{https://ir.linkedin.com/in/farzad-sadeghi-08426277}{Linkedin}} My Linkedin page.\\[5pt]
  {\bf \href{https://github.com/terminaldweller}{Github}} My Github page.\\[5pt]
  {\bf \href{https://github.com/terminaldweller/hived}{Hived}} My personal tiny high-performance server written in Go.\\[5pt]
  {\bf \href{https://github.com/terminaldweller/cgrep}{Cgrep}} Grep for C-family source files.\\[5pt]
  {\bf \href{https://terminaldweller.github.io/mutator/}{Mutator}} An experimental suite of tools aimed at C-family development written C++,C and Lua.\\[5pt]
  \href{https://github.com/terminaldweller/faultreiber}{Faultreiber} generates a binary file parser in C using an XML description file.\\[5pt]
  \href{https://github.com/terminaldweller/luatablegen}{Luatablegen} generates C code that wraps C structures as Lua tables using an XML description file.\\[5pt]
  {\bf \href{https://github.com/terminaldweller/dwasm}{Dwasm}} A WASM dump script written in python.\\[5pt]
  {\bf \href{https://github.com/terminaldweller/delf}{Delf}} An ELF dump script in python.\\[5pt]

  \section*{Referene}
  {\bf Jason Teutsch} jt@truebit.io\\[5pt]
  {\bf Francesco Zulliani} francesco.zuliani@neat.it\\[5pt]

\end{multicols}
\end{document}

