\documentclass[10pt]{article}
\usepackage{array, xcolor}
\usepackage[margin=3cm]{geometry}
\usepackage{longtable}
\usepackage{makecell}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
}
\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.2\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\title{\bfseries\Huge Farzad Sadeghi}
\author{farzadsadeghi@protonmail.ch}
\date{2020/03/31}
\begin{document}
\maketitle
\begin{center}
  \begin{minipage}[ht]{0.2\textwidth}{\centering}
  \vspace*{\fill}
  \centering
  Tehran, Iran\\
  +99 9999 9999999
  \centering
  \vspace*{\fill}
  \end{minipage}
\end{center}

\vspace{5mm}
\hrule
\vspace{5mm}

\section*{Professional Experience}
\begin{longtable}{L!{\VRule}R}
  {\bf Feb. 2019--Now}\\16 months&{\bf Maharan International (Tehran, Iran)}\\
  &Requirement manager, designer and developer and tooling.\\[5pt]
  & \\
  & \\
  {\bf July 2017--Nov. 2017}\\5 months&{\bf Truebit (Remote, 3 time-zones)}\\
  &Developed Truebit's WASM interpreter, smart contracts and CI. Also researched distributed storage networks for Truebit’s needs which included IPFS and Ethereum's swarm.\\[5pt]
  & \\
  & \\
  {\bf Sept. 2016--Nov. 2016}\\2 months&{\bf Iranian Electronics Industry Engineering Corp (Tehran, Iran)}\\
  & The role primarily included devising the coding standard and style for the company plus some general consultancy on embedded software development.\\[5pt]
  & \\
  & \\
  {\bf May 2016--July 2016}\\3 months&{\bf NEAT (Rome, Italy)}\\
 &Wrote an automatic refactoring tool using Clang(Libtooling) in C++. The tool would be the last piece of an automated model-driven development process for safety-critical systems.\\[5pt]
  & \\
  & \\
 {\bf July 2014--March 2016}\\21 months&{\bf Crouse (Tehran, Iran)}\\
  & Embedded software developer, Safety-critical applications: Implementation of the DSP algorithm, testing, automation and tooling. The Software team’s ISO 26262 representative. Helped develop the work-flow for the team by adopting and adapting Code Reviews, FMEA and FTA for software and tooling alongside some best practices and defensive C programming guidelines. Studied AUTOSAR's SWC and RTE specifications.\\[5pt]
  & \\
  & \\
  {\bf August 2010--March 2012}\\20 months&{\bf Safir Language Academy (Tehran, Iran)}\\
  & English Teacher - Later on specifically IELTS teacher.\\[5pt]
\end{longtable}

\vspace{5mm}
\hrule
\vspace{5mm}

\section*{Role Breakdown}
\begin{longtable}{L!{\VRule}R}
  {\bf ERTMS / ETCS DMI Development}& Derived software requirements from the system requirements, effectively splitting them into two components. Designed and implemented the software for the component on the kernel side. Wrote a tool that made the requirements' traceability files by gathering special comments from the C source files. Wrote a tool that determines all the sub-fields of aggregate types used in the function and the functions it calls(required for testing).
  \\[5pt]&\\
  {\bf Embedded Safety-Critical Development}& Wrote the SRS and the SDD for the DSP algorithm, then implemented the DSP algorithm for a safety-critical hard real-time embedded system.
  \\[5pt]&\\
  {\bf Code Generation}& \begin{itemize}
    \vspace{-\baselineskip}
    \item Wrote A tool that generates binary file (WASM, ...) parsers in C.
    \item Wrote another tool that generates the C code necessary to add a C structure to Lua as a Lua table.
    \end{itemize}
  \\[5pt]
  {\bf Automation and Tooling}& \begin{itemize}
    \vspace{-\baselineskip}
    \item Developed a Misra-C:2004 rule checker(open-source project) using Clang's Libtooling.
    \item Developed a source code obfuscation tool(open-source project) using Clang's Libtooling.
    \item Developed an interactive CLI tool aimed at object code manipulation(open-source project) in C++/C with Lua as it's scripting language. The tool also has Python embedded in it for rapid prototyping.
    \item Automated the traceability matrix generation using libclang's Python bindings.
    \item Automated the regression testing for a project I was involved in.
    \item Automated the calculation of the WCET for all implemented functions through the use of of a Python script and an XML description file.
    \end{itemize}
  \\[5pt]
  {\bf Automatic Refactoring}& Wrote an automatic refactoring tool using Clang's Libtooling for C.\\[5pt]
  & \\
  {\bf Defensive Programming / Safety-Aware Software Design}& Studied/Implemented defensive programming practices, coding style and guidelines. Explored the use of FMEA and FTA for the software domain.\\[5pt]
  & \\
  {\bf AUTOSAR}& Studied AUTOSAR SWC and RTE.\\[5pt]
  & \\
  {\bf ISO 26262}& Studied the software section of the standard. I was also the software's group's representative for the study/review meetings held with the hardware and system teams on ISO 26262.\\[5pt]
\end{longtable}

\vspace{5mm}
\hrule
\vspace{5mm}

\section*{Programming Languages}
\begin{tabular}{L!{\VRule}R}
  {\bf Languages}&C, C++\\[5pt]
  & \\
  {\bf Scripting Languages}&Python, Lua\\[5pt]
  & \\
  {\bf Other}&Bash, AWK, Make\\[5pt]
\end{tabular}

\vspace{5mm}
\hrule

\section*{Skills}
\begin{tabular}{L!{\VRule}R}
  {\bf Software Design}& Safety-aware software design.\\[5pt]
  & \\
  {\bf Requirement Analysis}& Derived the functional and technical software requirements from the ERTMS/ETCS DMI system requirements for our implementation.\\[5pt]
  & \\
  {\bf CI}& Appveyor for windows(cygwin-only) and TrvisCI for linux.\\[5pt]
  & \\
  {\bf UML}& Requirement Modelling.\\[5pt]
  {\bf Clang}& Libtooling and libclang.\\[5pt]
\end{tabular}

\vspace{5mm}
\hrule

\section*{Languages}
\begin{tabular}{L!{\VRule}R}
  {\bf English}&{\bf Native-like}\\
  {\bf Persian}&{\bf Native}\\
  {\bf Azerbaijani}&{\bf Native}\\
  German&Intermediate\\
\end{tabular}

\vspace{5mm}
\hrule
\vspace{5mm}

\section*{Education}
\begin{tabular}{L!{\VRule}R}
  2007--2013& Bachelor's in Electrical Engineering, Iran University of Science and Technology, Tehran, Iran.\\[5pt]
  &{\bf Thesis}: Determining the frequency of an audio signal using phase derivation in real time, design and implementation using an FPGA.
\end{tabular}

\vspace{5mm}
\hrule
\vspace{5mm}

\section*{Links}
\begin{tabular}{L!{\VRule}R}
  {\bf \href{https://ir.linkedin.com/in/farzad-sadeghi-08426277}{Linkedin}}& My Linkedin page.\\[5pt]
  {\bf \href{https://github.com/terminaldweller}{Github}}& My Github page.\\[5pt]
  {\bf \href{https://github.com/terminaldweller/cgrep}{Cgrep}}& Grep for C-family source files.\\[5pt]
  {\bf \href{https://terminaldweller.github.io/mutator/}{Mutator}}& An experimental suite of tools aimed at C-family development.\\[5pt]
  {\bf Faultreiber}&\href{https://github.com/terminaldweller/faultreiber}{Faultreiber} generates a binary file parser in C using an XML description file.\\[5pt]
  {\bf Luatablegen}&\href{https://github.com/terminaldweller/luatablegen}{Luatablegen} generates C code that wraps C structures as Lua tables using an XML description file.\\[5pt]
  {\bf \href{https://github.com/terminaldweller/dwasm}{Dwasm}}& A WASM dump script written in python.\\[5pt]
  {\bf \href{https://github.com/terminaldweller/delf}{Delf}}& An ELF dump script in python.\\[5pt]
\end{tabular}

\vspace{5mm}
\hrule
\vspace{5mm}

\section*{Referene}
\begin{longtable}{L!{\VRule}R}
  {\bf Jason Teutsch}& jt@truebit.io\\[5pt]
  {\bf Francesco Zulliani}& francesco.zuliani@neat.it\\[5pt]
\end{longtable}

\end{document}

